Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-08 cvpr2018.tex
12th

%%%%%%%%% TITLE
\title{Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents an novel method to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions, which is an effective end-to-end trainable single stream (vanilla-like) network that can generate high resolution images (e.g. $512^2$). Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial training to regularize intermediate representations in order to capture the complex image statistics. We present an intuitive as well as extensile network architecture to push generated images to high resolutions as well as preserve semantics and details. 
We apply multi-purpose adversarial learning at multiple nested scales to encourage more effective multimodal (i.e. image and text) information alignment in order to enhance generators to approach real distributions. 
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts.

@@

%%%%%%%%% BODY TEXT
\section{Introduction}
Generating photographic image conditional on arbitrary semantic description is an important problem in generative model research \cite{reed2016generative}. However, insufficient methods have been successfully developed to address this task due to its particular challenges. Text-to-image synthesis is similar to conventional generative tasks, which aim to translate a low-dimensional embedding  to a much more complex RGB image space.  Differently, the embedding space of the former is induced by semantic descriptions. Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts of descriptions but also fine-grained descriptive details in image pixels.

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} is th first to address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images, with two separate stage training. Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting semantic description. But its high resolution synthesis ability is unclear. 
At present, how to train from the low-dimensional text space to synthesize high resolution and diverse images in an end-to-end manner is still an open and attractive question.

We outline several empirical reasons for the challenges of text-to-image synthesis using GANs. The first is the fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. 
The second is the huge pixel space in high resolution images \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as preserve semantic consistency. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these outlined problems, in this paper, we propose a novel fully end-to-end method that can directly model high resolution image statistics and generate semantic consistent and photographic image up to $512^2$ resolution. The contributions are described follows.

Our generator is a more like simple vanilla-like GAN, without needing any inside text conditioning \cite{han2017stackgan} or image label supervision \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high resolution image space, our insight is to leverage hierarchical representations with additional implicit constraints. 
We introduce accompanying hierarchically-nested objective at intermediate layers to play adversarial games to encourage the generator approaching real distribution. 
We also propose a generator network structure design to cooperate our multi-scale nested discriminators more effectively.
To better make use of image and text information in GAN training, 
\textcolor{red}{we enforce nested discriminators at different scales can simultaneously differentiate real and fake, image-text pairs, images, and patches.}
This multi-purpose conditional adversary is mutually beneficial to allow each only focuses on respect duties. 
%It is a regularization to limit the discriminators to use unexpected information to make decision. 
We validate our proposed method on three datasets, i.e. CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale COCO datasets \cite{lin2014microsoft}. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts. All source code will be released.

\section{Related Work}
We discussed related methods as well as further clarify the novelty of our method comparing with them.

Deep generative models grows wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative} introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy to image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128^2$ resolution images. StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a pretrained ImageNet CNN \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.

Learning a continuous mapping from low-dimensional embeddings to complex real data distribution is a long-standing problem. Although GANs have made significant progressive, there are still many  unsolved difficulties, e.g. training instability and high resolution. Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or multiple discriminators  \cite{metz2016unrolled,durugkar2016generative,yang2017lr}. While our method does not use any extra information apart from training paired text and images. Moreover, it is easy to see the training difficulty grows significantly as targeting image resolution increases.

@@

To synthesize high resolution images, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear \cite{han2017stackgan}. Recently, Karras \cite{} show a progressive training of GANs to enable high resolution image generation. Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which enables end-to-end high resolution image synthesis.

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. 
Our hierarchically-nested adversarial adversarial objective is partially inspired by supervised CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. 
%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.   
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{} \label{fig:archs}
\end{figure}

%
%
%
%\subsection{Summarize different architectures}
%refer to HED.
\begin{figure}[t]
	\centering
%	\includegraphics[width=0.48\textwidth]{}
	\caption{} \label{fig:archs-compare}
\end{figure}

\section{Method}
Figure \ref{fig:archs} illustrate the overall method.

\section{Preliminary}
\subsection{Generative Adversary Network}
Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game. The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$, where the optimal $G$ and $D$ can be obtained by 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, {D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ V(D, G)
\end{split}
\end{equation}

%\begin{equation}
%\label{game}
%\begin{split}
%\underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
%&\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
%\end{split}
%\end{equation}
%where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
%In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
%In this paper, we replace the negative log likelihood loss with a least square objective\cite{lsgan}.

Conditioned GAN \cite{isola2016image} is a variation of traditional GAN where both the generator network $G$ and discriminator network $D$ are conditioned on an additional condition vector besides the noise vector. In this paper, we consider the task of training a deep  generative adversarial network conditioned on the embedding of the text descriptions of the images.

\section{Method}
Figure \ref{fig:archs} illustrate the overall method.
%To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective Hierarchically-nested Generative Adversarial Network.
Our approach is to train both generator and discriminator conditioned on sentence embedding vectors. We leverage functional loss for discriminator and hierarchically nested side outputs as hierarchical supervision for both generator and discriminator to achieve our goal of generating photo-realistic images from text descriptions.

In general, the generator takes text embedding and random noise vector as input and synthesis images at different scales (e.g, $64\times64$, $128\times128$, $256\times256$). The discriminator, on the other hand, is trying to judge the pair of synthesized images and the corresponding text embedding as fake pairs as well as differentiating the real images from the fake images. $G$ and $D$ are optimized alternatively until converges.

\textbf{Notation } 
We denote the training data set by $S=\{({X}^n, {T}^n),n=1,...,N\}$, where $X^n$ is the $n-$th training image, and $T^n={t^1,...,t^m}$ as $m$ text descriptions corresponds to $X^n$.

Since we obtain the text embedding vector  using the per-trained char-rnn text encoder provided in \cite{reed2016generative}. For simplicity, we do not differentiate text description and it's corresponding text embedding vector in this paper.  Our goal is to learn a generator $G$ that could produce high resolution images of high visual quality as well as variability giving an input text description $t$.

The input to $G$ compress input sentence embedding, and one noise input.
Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively. Please note that, $G$ has multiple branches and generates multiple images of different sizes. For each image size, we have a distinct discriminator $D$ associated with it. 
%For simplicity, we only describe one image size.

The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_{img}: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware pair discriminator $D_{pair}: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$.

\textbf{Variational text embedding } Following the practice of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(t), \Sigma(t) )$, in which the mean $\mu(t)$ and the diagonal covariance matrix $\Sigma(t)$ are non-linear transformation of the original text embedding $t$. This type of conditional augmentation technique can be used to inject randomness into the text embedding vector $t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}. In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.

\subsection{Hierarchical Deep Supervision}
Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.

Our architecture of $G$ consists of a single stream network with additional multiple side outputs. This architecture resemble the previous proposed method in edge detection\cite{xie2015holistically} and classification\cite{lee2015deeply}, which demonstrate that additional supervision to  hidden layers can improve model generalization and boost optimization.  We conjecture that adding hidden layer supervision using side outputs can act as a regularizer to the hidden space of $G$, which reduces the over-fitting issue and provide a short path for the error signal.

Given a random Gaussian noise  $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$ and a text description embedding $t$  $G$ will generate multiple side outputs,
\begin{equation}
\label{side}
\begin{split}
	o_1,...,o_s = G(t, z)	   
\end{split}
\end{equation}
where $s$ is the total number of side outputs, please note that the dimension of $o_1,..,o_s$ increase gradually (e.g., 64$\times$64, 128$\times$128, and 256$\times$256). For simplicity, we denote $o=\{o_1,...,o_s\}$.  Denote $\mathcal{X}^i = \{X^i_1, .. X^i_s\}$ as the pyramid of  resized images constructed from original image $X^i$.

For each $o_i$, a distinct discriminator $D_i$ is assigned to compete with it. Denote $\mathcal{D}=\{D_1, ..., D_o\}$ as the whole set of discriminators.
We aim to solve the following optimization problem:

\begin{equation}
\label{equ:optim}
\begin{split}
  G^*, \mathcal{D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(G,\mathcal{D}, \mathcal{X}, \bm{T})
\end{split}
\end{equation}
where $\mathcal{D}^*$ compresses the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.

Please note that in this setting, one generator competes with multiple discriminators. And each discriminators does not share weights with each other, thus giving them the flexibility to focus on learning different discriminative features.

In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images. 
Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than stackGan\cite{han2017stackgan}. This type of side output is also proven useful because it allows short path between image supervision information to the hidden feature maps, which could potentially helps training.

>>>>

%%%%%%%%% TITLE
\title{Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel method to deal with the challenging task of generating images conditioned on semantic image descriptions. We propose an effective end-to-end trainable single-stream network that can generate photographic high-resolution images (up to $512^2$). Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics. We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions. 
We adopt a multi-purpose adversarial learning strategy at multiple nested hierarchical side outputs to encourage more effective multimodal (i.e. image and text) information alignment in order to guarantee semantic consistency and image fidelity simultaneously. 
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts.

@@

%%%%%%%%% BODY TEXT
\section{Introduction}
Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}. However, insufficient methods have been developed to successfully address this task due to its particular challenges. It is a special case of generative learning tasks, which aim to map a low-dimensional embedding to a complex RGB image space. Differently, the embedding space of the former is induced by semantic descriptions. Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts of descriptions but also fine-grained descriptive details in image pixels.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.48\textwidth]{figure/intro.pdf}
%	\vspace{-.7cm}
	\caption{Overview of our method. It contains a single-stream generator and several hierarchically-nested discriminators and is trained end-to-end to generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} %\vspace{-.2cm}
\end{figure}

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images, with two separate stage training. Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting description. But its high-resolution synthesis ability is unclear. 
At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in an end-to-end manner is still an open and attractive question.

We outline several empirical reasons for the challenges of text-to-image synthesis using GANs. The first is the fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. 
The second is the huge pixel space in high-resolution images \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these outlined problems, in this paper, we propose a novel fully end-to-end method that can directly model high-resolution image statistics and generate semantic consistent and photographic image up to $512^2$ resolution. The contributions are described as follows.

Our generator resembles a simple vanilla-like GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints. 
We introduce accompanying hierarchically-nested objectives at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution. 
We also propose a novel generator convolutional neural network (CNN) framework to cooperate with our nested discriminators more effectively.
To better make use of image and text information in GAN training, 
\textcolor{red}{we enforce nested discriminators at different hierarchies can simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake whole images or image patches.}
This multi-purpose conditional adversary is mutually beneficial to allow each only focuses on its respect duties. 
%It is a regularization to limit the discriminators to use unexpected information to make decision.

We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts. All source code will be released.

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.95\textwidth]{figure/views2.pdf}
	\vspace{-.2cm}
	\caption{Overviews of some typical GAN frameworks. \textbf{A} decomposes tasks multi-stage GANs \cite{han2017stackgan,denton2015deep}. \textbf{B} uses multiple discriminators with one generator \cite{durugkar2016generative,tu_etal_nips17_d2gan}. \textbf{C} progressively trains symmetric discriminators and generators \cite{Karras2017progressive,huang2016stacked}. \textbf{A} and \textbf{C} can be viewed as decomposing high-resolution tasks to multi-stage low-to-high resolution tasks.  \textbf{D} is our proposed framework that uses a single-stream generator with hierarchically-nested discriminators trained end-to-end.} \label{fig:archs-review}
\end{figure*}

\section{Related Work}
We discussed related work and further clarify the novelty of our method by comparing with them.

Deep generative models attract wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative}  is th first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy for image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis, which uses extra information to help generate $128^2$ resolution images. StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a CNN pretrained on ImageNet \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.

Learning a continuous mapping from low-dimensional embeddings to a complex real data distribution is a long-standing problem. Although GANs have made significant progress, there are still many  unsolved difficulties, e.g. training instability and high-resolution extensions. Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or multiple discriminators  \cite{metz2016unrolled,durugkar2016generative,yang2017lr}. \textit{While our method does not use any extra information apart from training paired text and images.} Moreover, it is easy to see the training difficulty increases significantly as targeting image resolution increases.

@@

To synthesize high-resolution images, cascade networks are useful to decompose original difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
Denton \etal \cite{denton2015deep} train a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and the output from last level of the pyramid, and push up the output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method needs multiple symmetric bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear. Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for high-resolution image generation (Figure \ref{fig:archs-review} C). \textit{Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. 
\textit{Our hierarchically-nested adversarial objective is inspired by CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. }
%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.

%
%
%\subsection{Summarize different architectures}
%refer to HED.

%\section{Preliminary}
%\subsection{Generative Adversary Network}
%Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game. The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$, where the optimal $G$ and $D$ can be obtained by 
%\begin{equation}
%\label{equ:GAN}
%\begin{split}
%G^*, {D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ V(D, G)
%\end{split}
%\end{equation}
%
%%\begin{equation}
%%\label{game}
%%\begin{split}
%%\underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
%%&\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
%%\end{split}
%%\end{equation}
%%where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
%%In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
%%In this paper, we replace the negative log likelihood loss with a least square objective\cite{lsgan}. 
%
%Conditioned GAN \cite{isola2016image} is a variation of traditional GAN where both the generator network $G$ and discriminator network $D$ are conditioned on an additional condition vector besides the noise vector. In this paper, we consider the task of training a deep  generative adversarial network conditioned on the embedding of the text descriptions of the images.

\section{Method}
%Figure \ref{fig:archs} illustrate the overall method.

\subsection{Adversarial objective basics}
In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate realistic images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
%where the optimal $G$ and $D$ can be obtained by 
%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G)
\end{split}
\end{equation}
where the loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions.

%Conditioned GAN \cite{isola2016image} is a variation of traditional GAN where both the generator network $G$ and discriminator network $D$ are conditioned on an additional condition vector besides the noise vector. In this paper, we consider the task of training a deep generative adversarial network conditioned on the embedding of the text descriptions of the images.

%To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective Hierarchically-nested Generative Adversarial Network.
%Our approach is to train both generator and discriminator conditioned on sentence embedding vectors. We leverage functional loss for discriminator and hierarchically nested side outputs as hierarchical supervision for both generator and discriminator to achieve our goal of generating photo-realistic images from text descriptions.  
%
%In general, the generator takes text embedding and random noise vector as input and synthesis images at different scales (e.g, $64\times64$, $128\times128$, $256\times256$). The discriminator, on the other hand, is trying to judge the pair of synthesized images and the corresponding text embedding as fake pairs as well as differentiating the real images from the fake images. $G$ and $D$ are optimized alternatively until converges.
%
%
%\textbf{Notation } 
%We denote the training data set by $S=\{({X}^n, {T}^n),n=1,...,N\}$, where $X^n$ is the $n-$th training image, and $T^n={t^1,...,t^m}$ as $m$ text descriptions corresponds to $X^n$. 
%
%Since we obtain the text embedding vector using the per-trained char-rnn text encoder provided in \cite{reed2016generative}. For simplicity, we do not differentiate text description and it's corresponding text embedding vector in this paper.  Our goal is to learn a generator $G$ that could produce high resolution images of high visual quality as well as variability giving an input text description $t$.  
%
%The input to $G$ compress input sentence embedding, and one noise input.
%Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively. Please note that, $G$ has multiple branches and generates multiple images of different sizes. For each image size, we have a distinct discriminator $D$ associated with it. 
%%For simplicity, we only describe one image size.  
%
%The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_{img}: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware pair discriminator $D_{pair}: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$. 
%
%\textbf{Variational text embedding } Following the practice of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(t), \Sigma(t) )$, in which the mean $\mu(t)$ and the diagonal covariance matrix $\Sigma(t)$ are non-linear transformation of the original text embedding $t$. This type of conditional augmentation technique can be used to inject randomness into the text embedding vector $t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}. In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.

\subsection{Hierarchical-nested adversarial objectives}
%Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
Numerous methods have demonstrated a variety of ways to build GANs for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
Our method explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features to learn a stronger generator $\mathcal{G}$. 
The hierarchically-nested objectives 
%We conjecture that adding hierarchical adversarial objective using side outputs can
act as regularizers to the hidden space of $\mathcal{G}$, which can reduce the training instability and also offer a short path for better error signals.

The proposed $\mathcal{G}$ is a network (see Section 3.4), with $s{-}1$ side outputs at the intermediate layers:

%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.  
\begin{equation}
\label{side}
X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
\end{equation}
where $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise and $\bm t\sim p(data)$ denotes sentence embedding vector in the real training data distribution. $\mathcal{G}$ produces $s-1$ side size-growing image outputs and a final output $X_s$ with the highest resolution.

%$\mathcal{X}^i = \{X^i_1, .. X^i_s\}$ are side output
%Given $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$ and a text description embedding $t$, 
%$G$ generates $s$ side outputs using intermediate layers, $o=\{o_1,...,o_s\}$,
%Note that the dimension of $o_1,..,o_s$ increases according to the resolution
%(e.g., 64$\times$64, 128$\times$128, and 256$\times$256). 
%Denote $\mathcal{X}^i = \{X^i_1, .. X^i_s\}$ as the pyramid of resized images constructed from original image $X^i$.  
%Denote $\mathcal{D}=\{D_1, ..., D_o\}$ as the whole set of discriminators.
%e aim to solve the following optimization problem:
